Unifying quasars with clumpy wind models

### 2015-09-01 paper.tex
few more changes

When comparing BALQSO and quasar composites, it is apparent
that they possess remarkably similar line strengths and widths 
\citep[e.g.][]{reichard2003}.
This presents a challenge to our model, as well as the geometric 
unification picture in general.
Limb darkening and foreshortening causes the disc continuum emission to be 
strongly anisotropic, yet the line emission in our models is much more isotropic. 
This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
To construct a scenario where emission 
line equivalent widths are comparable at all inclinations requires 
significant fine-tuning when considering a classical thin disc. 
An alternative, simpler solution is that the emergent continuum is roughly isotropic.

General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
To generate GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
The output flux at three different wavelengths
as a function of inclination for an \agn\ model with the same disc and BH parameters
as our clumpy wind model is shown in figure~\ref{fig:f2000}.
The effects of GR on an AGN disc are much less extreme 
in the UV portion of the spectrum than the calculations
by \cite{zhang1997} for the X-rays in X-ray binaries.
As a result, the disc emission is still strongly anisotropic.
GR alone therefore cannot explain the line ratio trends in quasars by making the disc
emit more isotropically.
This supports the findings of \cite{risaliti2011}, who find that EW distributions 
in quasars are consistent with anisotropic emission from optically thick, 
disc-like structures for {\em both} the continuum source and BLR. 
We will explore these ideas further in a future study.

>>>>

When comparing BALQSO and quasar composites, it is apparent
that they possess remarkably similar line strengths and widths 
\citep[e.g.][]{weymann1991,reichard2003}.
This presents a challenge to our model, as well as the geometric 
unification picture in general.
Limb darkening and foreshortening causes the disc continuum emission to be 
strongly anisotropic, yet the line emission in our models is much more isotropic. 
This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
To construct a scenario where emission 
line equivalent widths are comparable at all inclinations requires 
significant fine-tuning when considering a classical thin disc. 
An alternative, simpler solution is that the emergent continuum is roughly isotropic.

General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.
To generate GR disc spectra, we use the code \agn.\citep{hubeny2000,davis2007}. 
The output flux at three different wavelengths
as a function of inclination for an \agn\ model with the same disc and BH parameters
as our clumpy wind model is shown in figure~\ref{fig:f2000}.
The effects of GR on an AGN disc are much less extreme 
in the UV portion of the spectrum than the calculations
by \cite{zhang1997} for the X-rays in X-ray binaries.
As a result, the disc emission is still strongly anisotropic.
GR alone therefore cannot explain the line ratio trends in quasars by making the disc
emit more isotropically. This supports the findings of \cite{risaliti2011}, 
who find that EW distributions in quasars are consistent with anisotropic emission 
from optically thick, 
disc-like structures for {\em both} the continuum source and BLR. 
If this is the case, it has a dramatic affect on the intrinsic
BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
We will explore these ideas further in a future study.
